---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dev = "ragg_png",
  fig.width = 8,
  dpi = 300
)
```

# mpsTemplates

<!-- badges: start -->
[![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
[![R-CMD-check](https://github.com/mps9506/mps-templates/workflows/R-CMD-check/badge.svg)](https://github.com/mps9506/mps-templates/actions)
<!-- badges: end -->

```{r}
library(ggplot2)
library(mpsTemplates)
ggplot(cars) +
  geom_point(aes(speed, dist)) +
  theme_mps_noto() +
  labs(title = "Cars", subtitle = "Speed and stopping distance",
       caption = "Ezekiel, M (1930) Methods of Correlation Analysis",
       x = "Speed [mph]",
       y = "Stopping Distance [ft]")
```



## pkgdown
The package includes some pkgdown template files intended for use by my packages.

To use, add/edit _pkgdown.yaml in the package root directory:

```yaml
template:
  package: mpsTemplates
  bootstrap: 5

navbar:
  type: light
  bg: light
  structure:
    right: [search, github]
```   

AND add the following to the DESCRIPTION:
```
Config/Needs/website: mps9506/mpsTemplates
```

Use rlibs Github Action to build the pkgdown documentation:
```{r eval=FALSE}
usethis::use_github_action("pkgdown")
```

## rmarkdown

The package includes the following rmarkdown templates:

 - *mps pdf Cormorant template*: Intended for pdf reports.


These are available in the RStudio New -> Rmarkdown selector after installing this package.

## bookdown

The package include the following project:

 - *mps Bookdown Single Page Website*: Intended for single page websites hosted on github pages
 
 These are available by loading the package and selecting "New Project" -> "New Directory" -> "mps Github Pages Website"
 
 

