---
title: "Template"
author: "Michael Schramm"
date: "`r Sys.Date()`"
github-repo: mps9506/mps-templates
bibliography: bibliography.bib
biblio-style: "apalike"
link-citations: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = "ragg_png",
                      fig.retina = 2)
library(mpsTemplates)
set.seed(101)
```


Use this as a template for single page bookdown sites hosted on github.

Setup github actions to knit on push and rendered docs get pushed to the `gh-pages` branch:

```{r eval=FALSE, echo=TRUE}
## Assumes that the project is created with git initiated and github is setup

## Need to initiate renv and push the lockfile to main branch before building.

## update this as packages are added
usethis::pr_init("use renv")
renv::snapshot()
gert::git_add(".")
gert::git_commit("add renv lockfile")
usethis::pr_push() ## browser should open to create pull request
usethis::pr_finish() ## cleanup

## do this once
usethis::pr_init("use bookdown")
usethis::use_github_action("bookdown")
gert::git_add(".")
gert::git_commit("add bookdown github action files")
usethis::pr_push() ## browser should open to create pull request
usethis::pr_finish() ## cleanup
```



# Chapter 1 {-}

To preview the book:
```{r eval=FALSE}
bookdown::render_book("document.Rmd")
```

blah blah [@rcore].

## Subheading

\begin{equation}
  \left(\prod_{i=1}^{n}y_i\right)^{\frac{1}{n}} =
  \exp\left[\frac{1}{n}\sum_{i=1}^n\log{y_i}\right],
  \quad \textrm{when} \quad y_1, y_2, ..., y_n > 0
  (\#eq:gmean)
\end{equation}


Cross reference equations by using `\@ref(eq:gmean")` see Equation \@ref(eq:gmean).

# Chapter 2 {-}

# References {-}
